<header style="text-align: center">

### 2019-05-19 report/report.Rmd
Add first figures to report

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

@@

>>>>

```{r setup, include = FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r}
bru <- 'EBBR'
event <- c('2016-02-28', '2016-03-01')
```
```{r, fig.align='center'}
ddr.map(data$real$routes[1:1000], autocenter = FALSE)
```

```{r, fig.align='center'}
ddr.times(data$real$flights, bru, event)
```

@@

- N flights vs. time with orig/dest at EBBR
- N diverted flights vs. time with dest EBBR
